A linear inside-outside algorithm for detecting next generation sequencing errors in structured RNAs

### 2012-10-06 Recomb/introduction_RECOMB.tex

To benchmark our technique we use the 5S ribosomal RNA family,
 which is around $120$ nucleotides longs. We show

>>>>

The 5S ribosomal RNA family, $119$ nucleotides long,  was used to benchmark our method.
It is a prime example since it has been extensively used for phylogenetic
reconstructions~\cite{Hori1987} and its sequence has been recovered for over 8000 species
 (RFAM Id: \texttt{RF00001}).
 Using a leave one out strategy, we perform random distributed mutations on a sequence. We show that
\texttt{RNApyro} reconstructs the original sequence with an excellent accuracy.

The pseudo-energetic model and the algorithm is presented in Sec.~\ref{sec:methods}.
Details of the implementation and benchmarks are in Sec.~\ref{sec:results}. 
Future applications and a discussion are developed in Sec.~\ref{sec:conclusion}.
